A hierarchical approach for modelling X-ray beamlines. Application to a coherent beamline.

### 2019-06-17 paper-hierarchical.tex
rafael

\begin{table}\label{tab:SRW_results}
\centering
\caption{Calculated beam dimensions (FWHM, in nm) at the focal position for different models of focusing elements using SRW.}
\resizebox{\textwidth}{!}{%
\begin{tabular}{ccccc}
Focusing elements                 & Plane      &  Single electron & EBS         & ESRF-1       \\ \\
ideal lenses/ elliptical mirrors  & Horizontal &  8.53/9.54       & 12.71/11.56 & 17.75/12.41 \\
the same, with errors             & Horizontal &  9.36/10.61      & 13.20/12.52 & 17.78/15.71 \\
ideal lenses/ elliptical mirrors  & Vertical   &  7.11/7.26       & 8.40/9.02   & 8.24/8.77    \\
the same, with errors             & Vertical   &  7.44/8.46       & 8.66/9.87   & 8.52/9.66    \\                                            
\end{tabular}
}
\end{table}

@@

The combination of ray-tracing and wave optics methods used indicate that the focalized beam size due to  demagnification with mirrors (giving for EBS 10$\times$5~nm$^2$ analytically, 8.8$\times$4.5~nm$^2$ with ray-tracing) has to be corrected with diffraction effect (11.2$\times$8~nm$^2$ hybrid, 12.7$\times$9.2~nm$^2$ SRW) and then add the slope error effect. The slope errors do not blow up the size and kit it in the specifications range (11.4$\times$8.5~nm$^2$ hybrid \inred{13.6$\times$9.9~nm$^2$ SRW}). It is important to treat the slope errors correctly. Slope errors can be included in the ray-tracing using the data in Appendix~\ref{appendix:metrology} and applying specular reflection on the optical surface with errors. This is the standard model of including slope errors in SHADOW, using measured profiles or synthetic ones. It works well for the case of incoherent beams, but in our case, because of the high coherence of the beam the ray-tracing method (specular reflection) overestimates the blowing of the focal spot conducting to wrong results. Therefore the slope errors of the KB system have been considered using a ``wave optics approach'', as explained in Ref.~\cite{hybrid}. Here, the mirror height errors $z(x)$ are projected to the plane perpendicular to the propagation ($z(x) \sin \theta$, with $\theta$ the grazing angle). They introduce a phase shift $\psi$ in the wavefront phase proportional to the optical path $\psi = k z(x) \sin \theta $. This is the algorithm used in the simulations in Sections~\ref{level1}, \ref{srw_se} and \ref{srw_me}.

>>>>

\begin{table}\label{tab:SRW_results}
\centering
\caption{Calculated beam dimensions (FWHM, in nm) at the focal position for different models of focusing elements using SRW.}
\resizebox{\textwidth}{!}{%
\begin{tabular}{ccccc}
Focusing elements                 & Plane      &  Single electron & EBS         & ESRF-1       \\ \\
ideal lenses/ elliptical mirrors  & Horizontal &  8.53/9.54       & 12.71/11.56 & 17.75/12.41 \\
the same, with errors             & Horizontal &  9.36/10.61      & 13.20/12.52 & 17.78/15.71 \\
ideal lenses/ elliptical mirrors  & Vertical   &  7.22/7.94       & 8.66/9.38   & 8.90/10.11    \\
the same, with errors             & Vertical   &  7.70/8.90       & 8.42/9.14   & 8.90/9.86    \\                                            
\end{tabular}
}
\end{table}

@@

The combination of ray-tracing and wave optics methods used indicate that the focalized beam size due to  demagnification with mirrors (giving for EBS 10$\times$5~nm$^2$ analytically, 8.8$\times$4.5~nm$^2$ with ray-tracing) has to be corrected with diffraction effect (11.2$\times$8~nm$^2$ hybrid, 12.56$\times$9.38~nm$^2$ SRW) and then add the slope error effect. The slope errors do not blow up the size and kit it in the specifications range (11.4$\times$8.5~nm$^2$ hybrid 13.6$\times$9.14~nm$^2$ SRW). It is important to treat the slope errors correctly. Slope errors can be included in the ray-tracing using the data in Appendix~\ref{appendix:metrology} and applying specular reflection on the optical surface with errors. This is the standard model of including slope errors in SHADOW, using measured profiles or synthetic ones. It works well for the case of incoherent beams, but in our case, because of the high coherence of the beam the ray-tracing method (specular reflection) overestimates the blowing of the focal spot conducting to wrong results. Therefore the slope errors of the KB system have been considered using a ``wave optics approach'', as explained in Ref.~\cite{hybrid}. Here, the mirror height errors $z(x)$ are projected to the plane perpendicular to the propagation ($z(x) \sin \theta$, with $\theta$ the grazing angle). They introduce a phase shift $\psi$ in the wavefront phase proportional to the optical path $\psi = k z(x) \sin \theta $. This is the algorithm used in the simulations in Sections~\ref{level1}, \ref{srw_se} and \ref{srw_me}.
